A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-22 simulations.tex
Second draft complete

\section{Simulation Scenario}\label{simulations}
This section provides the simulation parameters for testing CSMA/ECA$_{\text{Hys+FS}}$ under two different traffic conditions, namely saturated and non-saturated. \textcolor{red}{We also provide details on how channel imperfections are modelled and what are its effects over the transmissions}. Further, the simulation of the clock drift effect, and the coexistence with CSMA/CA are also subjects to be addressed in this section.

	\subsection{Scenario details}
	Results are obtained by running multiple simulations over a modified version of the COST simulator~\cite{COST}, available at~\cite{sim:parameters}. PHY and MAC parameters are detailed in Table~\ref{tab:mac-params}. Some assumptions were made in order to test the performance at the MAC layer:

@@

	\textcolor{red}{\subsection{Channel errors}\label{channelErrorsDef}
	Channel errors are modelled by assigning a probability of a packet being corrupted by the channel, $p_e>0$. That is, in a single packet transmission there is probability $p_e$ that the transmission will not be acknowledged. If the transmission is an A-MPDU (like in the case of CSMA/ECA$_{\text{Hys+FS}}$), $p_e$ will affect each packet individually and independently. Therefore, an A-MPDU transmission will be considered a failure if all packets in the aggregation are affected by the channel error probability.}

>>>>

\section{Simulation Scenario}\label{simulations}
This section provides the simulation parameters for testing CSMA/ECA$_{\text{Hys+FS}}$ under two different traffic conditions, namely saturated and non-saturated. \textcolor{red}{We also provide details on how channel imperfections are modelled and what are its effects over the transmissions. Further, the simulation of the clock drift effect, Schedule Reset parameters, and the coexistence with CSMA/CA are also subjects to be addressed in this section.}

	\subsection{Scenario details}
	Results are obtained by running multiple simulations over a modified version of the COST simulator~\cite{COST}, available at~\cite{sim:parameters-TON}. PHY and MAC parameters are detailed in Table~\ref{tab:mac-params}. Some assumptions were made in order to test the performance at the MAC layer:

@@

	\textcolor{red}{\subsection{Channel errors}\label{channelErrorsDef}
	Channel errors are modelled by assigning a probability of a packet being corrupted by the channel, $p_e>0$. That is, in a single packet transmission there is probability $p_e$ that the transmission will not be acknowledged. If the transmission is an A-MPDU (like in the case of CSMA/ECA$_{\text{Hys+FS}}$), $p_e$ will affect each MPDU individually and independently. Therefore, an A-MPDU transmission will be considered a failure if all frames in the aggregation are affected by the channel error probability.}
